---
title: "Researcher Training and Development Sessions for 2023"
#subtitle: "Enrolment and Attendance Statistics by College (as of December 2023)"
#author: "Jen Beaudry"
#date: "19/10/2023"
output: pdf_document
editor_options: 
  chunk_output_type: console
header-includes:
  - \usepackage{caption}
  - \usepackage{titling}
    \setlength{\droptitle}{-2cm} # removes some of the white space above title
  - \pretitle{\begin{center}
    \includegraphics[width=1.5in, height=1.5in]{flinders-university-horizontal-master.png}\LARGE\\} # adds logo
  - \posttitle{\end{center}}
  - \usepackage{fancyhdr}
  - \fancypagestyle{plain}{\pagestyle{fancy}} # sets the footer on page 1
  - \pagestyle{fancy} # sets the footer on page 2 and beyond
  - \fancyhf{} # clears existing header & footer
  - \renewcommand{\headrulewidth}{0pt} # removes the line from the header
  - \fancyfoot[L]{Jen Beaudry} # my name in footer
  - \fancyfoot[R]{\thepage} # page number in foooter
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE,
                      include = FALSE, 
                      eval = FALSE)

```

```{r library, eval=TRUE}

library(here)
library(tidyverse)
library(kableExtra)
library(readxl)
library(janitor)
library(rmarkdown)
library(ggrepel) #for annotations in ggplot

```

```{r load ienrol data, eval=TRUE}

df_full <- read_csv(here::here("data", "2023_ienrol_data.csv"), lazy = FALSE) %>% 
  clean_names()

```

```{r delete sessions that did not run, eval=TRUE, include=FALSE}

# delete the sessions that were scheduled but not run [will need to compare to our training spreadsheet]
  # use the n_courses code in the next chunk to make it easy to figure out which sessions didn't run

df_remove1 <- df_full %>% 
  filter(course_name == "Open Research Practices" & event_num == "2")

df_remove2 <- df_full %>% 
  filter(course_name == "The Strategic Researcher") 

df_remove3 <- df_full %>% 
  filter(course_name == "Foreign Interactions Information for Researchers") 

df_remove4 <- df_full %>% 
  filter(course_name == "ARC DECRA Development Session")

df_remove5 <- df_full %>% 
  filter(course_name == "NHMRC Investigator Grants Information Session" & event_num == "1")

df_remove_a <- full_join(df_remove1, df_remove2)
df_remove_a <- full_join(df_remove_a, df_remove3)
df_remove_a <- full_join(df_remove_a, df_remove4)
df_remove_a <- full_join(df_remove_a, df_remove5)

df_full <- anti_join (df_full, df_remove_a)

rm(df_remove1, df_remove2, df_remove3, df_remove4, df_remove5, df_remove_a)

```


```{r clean data, eval=TRUE}

df <- df_full %>%
  select (c(course_name, event_num, first_name, last_name, fan, department, job_status, status)) 

# turn them into factors

cols <- c("course_name",
          "event_num",
             "department",
             "job_status",
             "status")

# recode status and department

df <- df %>% 
  dplyr::mutate(across(all_of(cols), ~factor(.))) %>% 
  dplyr::mutate(attendance_status = case_when (status == "attended" ~ "Attended", 
                                        status == "didnotattend" ~ "Did not attend")) %>% 
  dplyr::mutate(portfolio = case_when (grepl("Research", department) ~ "Portfolio of the Deputy Vice-Chancellor (Research)", #recode RDS as DVC(R)
                                    !grepl("College of", department) ~ "Other portfolios",
                                    department == "Other" ~ "Other",
                                    department == "Unknown" ~ "Other", 
                                    TRUE ~ as.factor(as.character(department))))


# summarise the data based on how many courses were held and how many folks attended each of the sessions

n_courses <- df %>% 
  filter(attendance_status == "Attended") %>% 
  count(course_name, event_num)


# this number will differ from the T&D spreadsheet because we have had attendees that are not in iEnrol

n_attendees <- df %>%
  filter(attendance_status == "Attended") %>% 
  count(fan, course_name, event_num)

# unique attendees 
n_unique_attendees <- n_distinct(n_attendees$fan)


# all attendees broken down by College

df_portfolios <- df %>% 
  filter (portfolio == "Other portfolios") %>% 
  count(department) %>% 
  arrange(-n)

n_portfolios <- unique(df_portfolios$department)



# Attendance status

attended <- df %>% filter(attendance_status == "Attended")
not_attended <- df %>% filter(attendance_status == "Did not attend")


```

## Summary 

In 2023, the Training, Development and Communication team in Research
Development and Support have offered `r nrow(n_courses)` information 
sessions and development workshops to researchers and research support
staff at Flinders University. 

We have had `r nrow(n_attendees)` people from Flinders attend the training and 
development sessions. Our actual attendance numbers for the year are larger (2467) 
because we allowed external researchers to join select sessions (e.g., Open 
Research sessions; ARC Outreach sessions, etc.). Of the `r nrow(n_attendees)` 
attendees, `r n_unique_attendees` were unique attendees, demonstrating 
that a large number of people from the Flinders research community are engaging in our program. 

The number of attendees at our sessions varied from `r min(n_courses$n)` in a 
hands-on ethics workshop to `r max(n_courses$n)` in a research grant writing workshop. 
The mean number of attendees at our sessions was `r round(mean(n_courses$n),0)` 
with a median of `r round(median(n_courses$n),0)`. 

Below, we break down our enrolments by Colleges and portfolio. Most of the 
professional staff who attended our training and development sessions were 
from the Portfolio of the Deputy Vice-Chancellor (Research). We collapsed all 
other portfolios in the University into a single "Other portfolios" category 
because of the large number of portfolios that our registrants represent 
(including Library, Information and Digital Services, and people who are not 
aligned with any portfolio in the ienrol system). 

# Breakdown by College and Portfolio

Below is a breakdown of how many people enrolled in 
these sessions across the Colleges and portfolios. The figure also represents
how many of those who enroled attended the sessions and how many enroled 
but did not attend the sessions. Overall, across all Colleges and 
portfolios, the average attendance rate for 
2023 was `r round(((nrow(attended)/(nrow(attended) + nrow(not_attended)))*100), 2)`%.

By far, the largest number of enrolments
and attendees were in the College of Medicine and Public Health, which is 
representative of the large number of researchers and research support staff in 
that College. The highest attendance rate was from staff in the Portfolio of the 
Deputy Vice-Chancellor (Research), which includes Research Development and Support 
and the Strategic Partnerships Team. 


\vskip 0.3in

\captionsetup[table]{labelformat=empty}


```{r plot the ienrol attendance rate, include = TRUE, eval=TRUE, fig.width = 15, fig.height = 9}

#combine sessions & attendees & attendance rate per portfolio
df_grouped <- df %>%
  count(portfolio, attendance_status) %>% 
    group_by(portfolio) %>% 
    mutate(att_pct = (n/sum(n)) *100) %>%
    mutate(enrol = sum(n))


# add in the attendance label here & rearrange it so it matches the data (which will be reordered in ggplot)
df_label <- df_grouped %>% 
   dplyr::mutate(
  perc_label = paste0(sprintf("\n\nAttendance rate = %1.1f", att_pct), "%"), 
  port_perc_label = paste(portfolio, perc_label)) %>% 
  filter(attendance_status == "Attended") %>% 
  arrange(n)


#use this to reorder the attendance factor within the ggplot code 
attend <- c("Did not attend", "Attended")


# plot it [this has attendance & non-attendance numbers & attendance rates in the names for the portfolios]
ggplot(df_grouped, aes(
  x = reorder(portfolio, n),
  fill = factor(attendance_status, levels = attend),
  y = n
)) +
  geom_bar(stat = "identity", colour = "black") +
  geom_text(aes(y = n,
                x = portfolio,
                label = n),
            position = position_stack(vjust = 0.5),
            size = 6) +
  coord_flip() +
  labs (title = "Attendance by College and Portfolios (2023)", 
        x = element_blank(),
        y = "Number of enrolments") +
  theme_classic() +
  theme(
    legend.title = element_blank(),
    legend.position = c(0.8, 0.2),
    title = element_text(size = 14, family="sans"),
    legend.text = element_text(size = 14, family="sans"),
    axis.text = element_text(size = 14, family ="sans"), 
    axis.title = element_text(size = 14, family = "sans") 
    ) +
  scale_fill_manual(
    values = c("#bfbfbf", "#90b8da"),
    labels = c("Did not attend", "Attended"),
    guide = guide_legend (reverse = TRUE)
  ) +
  scale_x_discrete(
    labels = df_label$port_perc_label) 


#ggsave(plot = last_plot(),filename = here::here("figures", "2023 attendance rates by portfolio.png"),
#       width = 15, height = 9, dpi = 300)

```



```{r plot the ienrol attendance, include = FALSE, eval=TRUE, fig.width = 15, fig.height = 9}

# count attendees rate per portfolio
df_attend <- df %>%
  filter(attendance_status == "Attended") %>% 
  count(portfolio)


# plot it [this has attendance numbers by the portfolios]
ggplot(df_attend, aes(
  x = reorder(portfolio, n),
  y = n
)) +
  geom_bar(stat = "identity", colour = "black", fill = "#90b8da") +
  geom_text(aes(y = n,
                x = portfolio,
                label = n),
            position = position_stack(vjust = 0.5),
            size = 6) +
  coord_flip() +
  labs (title = "Number of Attendees in Training & Development Sessions (2023)", 
        x = element_blank(),
        y = "Number of attendees") +
  theme_classic() +
  theme(
    title = element_text(size = 14, family="sans"),
    legend.text = element_text(size = 14, family="sans"),
    axis.text = element_text(size = 14, family ="sans"), 
    axis.title = element_text(size = 14, family = "sans") 
    ) +
  scale_fill_manual(
    values = "#90b8da"
  ) 
 # scale_x_discrete(
 #   labels = df_label$port_perc_label) 


ggsave(plot = last_plot(),filename = here::here("figures", "2023 attendance by portfolio.png"),
       width = 15, height = 9, dpi = 300)

```

\vskip 0.3in

```{r plot the ienrol attendance for unique attendees, include = TRUE, eval=TRUE, fig.width = 15, fig.height = 9}

# count attendees rate per portfolio
df_attend_unique <- df %>%
  filter(attendance_status == "Attended") %>% 
  distinct(fan, attendance_status, portfolio) %>% 
  count(portfolio)


# plot it [this has unique attendance numbers by the portfolios]
ggplot(df_attend_unique, aes(
  x = reorder(portfolio, n),
  y = n
)) +
  geom_bar(stat = "identity", colour = "black", fill = "#90b8da") +
  geom_text(aes(y = n,
                x = portfolio,
                label = n),
            position = position_stack(vjust = 0.5),
            size = 6) +
  coord_flip() +
  labs (title = "Number of Unique Attendees in Training & Development Sessions (2023)", 
        x = element_blank(),
        y = "Number of attendees") +
  theme_classic() +
  theme(
    title = element_text(size = 14, family="sans"),
    legend.text = element_text(size = 14, family="sans"),
    axis.text = element_text(size = 14, family ="sans"), 
    axis.title = element_text(size = 14, family = "sans") 
    ) +
  scale_fill_manual(
    values = "#90b8da"
  ) 
 # scale_x_discrete(
 #   labels = df_label$port_perc_label) 


ggsave(plot = last_plot(),filename = here::here("figures", "2023 unique attendance by portfolio.png"),
       width = 15, height = 9, dpi = 300)

```



```{r graveyard from plot the ienrol attendance, eval=FALSE}

#combine sessions & attendees & attendance rate per portfolio
df_grouped <- df %>%
  count(portfolio, attendance_status) %>% 
    group_by(portfolio) %>% 
    mutate(att_pct = (n/sum(n)) *100) %>%
    mutate(enrol = sum(n))

# add in the attendance label here
df_label <- df_grouped %>% 
   dplyr::mutate(
  perc_label = paste0(sprintf("\n\nAttendance rate = %1.1f", att_pct), "%"), 
  port_perc_label = paste(portfolio, perc_label)) %>% 
  filter(attendance_status == "Attended") %>% 
  arrange(n)

#vector_paste_vertical(df_label$port_perc_label)

# rearrange so it aligns with 
my.labels <-
  c(
    "College of Business, Government and Law \n\nAttendance rate = 72.2%",
    "College of Education, Psychology and Social Work \n\nAttendance rate = 64.1%",
    "College of Humanities, Arts and Social Sciences \n\nAttendance rate = 76.3%",
    
    "College of Nursing and Health Sciences \n\nAttendance rate = 67.9%",
    "College of Science and Engineering \n\nAttendance rate = 66.5%",
    "Deputy Vice-Chancellor (Research) \n\nAttendance rate = 83.4%",
    "Other portfolios \n\nAttendance rate = 70.0%"
    "College of Medicine and Public Health \n\nAttendance rate = 70.0%",
  )


#port_perc_label = paste(portfolio, perc_label)))

    # perc_label = ifelse(portfolio == "College of Medicine and Public Health", 
   #                      paste0(sprintf("\n\nAttendance rate = %1.1f", att_pct), "%"), ),
# paste(df_grouped$port_perc_label)

    # perc_label = ifelse(portfolio == "College of Medicine and Public Health", paste0("attendance rate = ", perc_label), perc_label))

#use this to reorder the factor within the ggplot code 
attend <- c("Did not attend", "Attended")
my.labels <- if_else(df_grouped$attendance_status == "Attended", df_grouped$port_perc_label, "")




# plot it [explain code here]



ggplot(df_grouped, aes(x = reorder(portfolio, n),
  fill = factor(attendance_status, levels = attend),
  y = n
)) +
  geom_bar(stat = "identity", colour = "black") +
  geom_text(
    aes(
      y = n,
      x = portfolio,
      label = n
    ),
    position = position_stack(vjust = 0.5),
    size = 3
  ) +
  coord_flip() +
  labs (x = element_blank(),
        y = "Count") +
  theme_classic() +
  theme(legend.title = element_blank(), 
        legend.position = c(0.8, 0.2), 
        legend.text = element_text(size = 14)) + 
  scale_fill_manual(values = c("#bfbfbf", "#90b8da"),
                 labels = c("Did not attend", "Attended"),
                   guide = guide_legend (reverse = TRUE)) +
  scale_x_discrete(labels = df_label$port_perc_label)


  geom_text(aes(
    label = ifelse(attendance_status == "Did not attend", "", perc_label) 
    # vjust = -2, 
    # hjust = -2
  ))
  
  
  
  scale_y_continuous(name = paste0(portfolio, perc_label))


  geom_text(aes(
    label = ifelse(attendance_status == "Did not attend", "", perc_label)),
    hjust = 5)


  geom_text(aes(
    label = ifelse(attendance_status == "Did not attend", "", (paste0(
        sprintf("attendance rate = %1.1f", att_pct), "%")))),
    position = position_stack(vjust = 1)) +
  scale_x_continuous(name = paste0(sprintf("%", portfolio, "\nattendance rate = %1.1f", att_pct), "%"))


# plot it [this works & shows the attendance rate on the bar & the total enrolment on the side]


f <- ggplot(df_grouped, aes(x = reorder(portfolio, n),
  fill = factor(attendance_status, levels = attend),
  y = n
)) +
  geom_bar(stat = "identity", colour = "black") +
  geom_text(
    aes(
      y = n,
      x = portfolio,
      label = ifelse(attendance_status == "Did not attend", "", (paste0(
        sprintf("%1.1f", att_pct), "%"
      )))
    ),
    position = position_stack(vjust = 0.5),
    size = 3
  ) +
  coord_flip() +
  labs (x = element_blank(),
        y = "Count") +
  theme_classic() +
  theme(legend.title = element_blank()) +
  scale_fill_manual(values = c("#bfbfbf", "#90b8da"),
                 labels = c("Did not attend", "Attended"),
                   guide = guide_legend (reverse = TRUE)) +
  geom_text(aes(
    label = ifelse(attendance_status == "Did not attend", enrol, "")),
    position = position_stack(vjust = 1.3))



```


```{r sessions by theme,eval=FALSE}

# decide whether I want the full data set (df_all) or just the sessions
  # we've run to date (df_run)
df <- df_run

# how many sessions per theme
theme <- df %>%
  group_by(Theme) %>%
  summarise(`Number of Sessions` = n()) %>%
  arrange (desc(`Number of Sessions`))

# make it look good
kable(theme, align = c('l', 'c'))

```


```{r attendees by theme, eval = FALSE}

# how many attendees per theme
attendees <- df %>%
  group_by(Theme) %>%
  summarise(`Number of Attendees` = sum(attended)) %>%
  arrange (desc(`Number of Attendees`))

# make it look good
kable(attendees, align = c('l', 'c'))

```


```{r sessions and attendees by theme, include=TRUE, eval = FALSE}

#combine sessions & attendees per theme
both <- df %>%
  group_by(Theme) %>%
  summarise(`Number of Sessions` = n(),
            `Number of Attendees` = sum(attended)) %>%
  arrange (desc(`Number of Attendees`)) %>% 
    adorn_totals("row")

# both <- both %>% 
#   adorn_totals("row")

# make it look good
kable(both, 
      booktabs = T,
      align = c('lcc'), 
      caption = "Training and Development Summary for 2022", 
      linesep = "\\addlinespace") %>% 
  kable_styling(latex_options = c("hold_position", "striped")) 

# %>% 
#   add_footnote("The Final Tally for 2021", 
#                notation = "none")

```


```{r sessions and names by theme}

# decide whether I want the full data set (df_all) or just the sessions
  # we've run to date (df_run)
df <- df_run

# how many sessions per theme
theme_sessions <- df %>%
  group_by(Theme) %>% 
  select(c(Theme, Session, attended)) %>% 
  arrange(Theme)

# make it look good
kable(theme_sessions, 
      booktabs = T,
      align = c('llc')) %>% 
        column_spec (column = 2, width = "12cm") %>% 
    kable_styling(latex_options = c("hold_position", "striped"))

```


```{r sessions and names by fund, include=TRUE}

# decide whether I want the full data set (df_all) or just the sessions
  # we've run to date (df_run)
df <- df_run

# how many sessions per theme
fund_sessions <- df %>%
  filter(Theme == "Fund and Apply") %>% 
  select(c(Session, attended)) %>% 
  arrange(desc(attended))

# make it look good
kable(
  fund_sessions,
  booktabs = T,
  linesep = "\\addlinespace",
  caption = "Fund and Apply Sessions",
  align = c('lc'),
  col.names = c("Session", "Number of Attendees")) %>%
  column_spec (column = 1, width = "12cm") %>%
  kable_styling(latex_options = c("hold_position", "striped"))

```

\clearpage

```{r sessions and names by comm, include=TRUE}

# decide whether I want the full data set (df_all) or just the sessions
  # we've run to date (df_run)
df <- df_run

# how many sessions per theme
comm_sessions <- df %>%
  filter(Theme == "Communicate") %>% 
  select(c(Session, attended)) %>% 
  arrange(desc(attended))

# make it look good
kable(
  comm_sessions,
  booktabs = T,
  linesep = "\\addlinespace",
  caption = "Communicate Sessions",
  align = c('lc'),
  col.names = c("Session", "Number of Attendees")) %>%
  column_spec (column = 1, width = "12cm") %>%
  kable_styling(latex_options = c("hold_position", "striped"))

```

```{r sessions and names by dvcr, include=TRUE}

# decide whether I want the full data set (df_all) or just the sessions
  # we've run to date (df_run)
df <- df_run

# how many sessions per theme
dvcr_sessions <- df %>%
  filter(Theme == "DVCR") %>% 
  select(c(Session, attended)) %>% 
  arrange(desc(attended))

# make it look good
kable(
  dvcr_sessions,
  booktabs = T,
  linesep = "\\addlinespace",
  caption = "DVC(R) Sessions",
  align = c('lc'),
  col.names = c("Session", "Number of Attendees")) %>%
  column_spec (column = 1, width = "12cm") %>%
  kable_styling(latex_options = c("hold_position", "striped"))

```

```{r sessions and names by ethics, include=TRUE}

# decide whether I want the full data set (df_all) or just the sessions
  # we've run to date (df_run)
df <- df_run

# how many sessions per theme
ethics_sessions <- df %>%
  filter(Theme == "Integrity and Ethics") %>% 
  select(c(Session, attended)) %>% 
  arrange(desc(attended))

# make it look good
kable(
  ethics_sessions,
  booktabs = T,
  linesep = "\\addlinespace",
  caption = "Integrity and Ethics Sessions",
  align = c('lc'),
  col.names = c("Session", "Number of Attendees")) %>%
  column_spec (column = 1, width = "12cm") %>%
  kable_styling(latex_options = c("hold_position", "striped"))

```

```{r sessions and names by consult, include=TRUE}

# decide whether I want the full data set (df_all) or just the sessions
  # we've run to date (df_run)
df <- df_run

# how many sessions per theme
consult_sessions <- df %>%
  filter(Theme == "Consultation") %>% 
  select(c(Session, attended)) %>% 
  arrange(desc(attended))

# make it look good
kable(
  consult_sessions,
  booktabs = T,
  linesep = "\\addlinespace",
  caption = "Consultation Sessions",
  align = c('lc'),
  col.names = c("Session", "Number of Attendees")) %>%
  column_spec (column = 1, width = "12cm") %>%
  kable_styling(latex_options = c("hold_position", "striped"))

```

```{r sessions and names by internal, include=TRUE}

# decide whether I want the full data set (df_all) or just the sessions
  # we've run to date (df_run)
df <- df_run

# how many sessions per theme
internal_sessions <- df %>%
  filter(Theme == "Internal") %>% 
  select(c(Session, attended)) %>% 
  arrange(desc(attended))

# make it look good
kable(
  internal_sessions,
  booktabs = T,
  linesep = "\\addlinespace",
  caption = "Internal Sessions for RDS Staff",
  align = c('lc'),
  col.names = c("Session", "Number of Attendees")) %>%
  column_spec (column = 1, width = "12cm") %>%
  kable_styling(latex_options = c("hold_position", "striped"))

```

```{r sessions and names by faststart, include=TRUE}

# decide whether I want the full data set (df_all) or just the sessions
  # we've run to date (df_run)
df <- df_run

# how many sessions per theme
fs_sessions <- df %>%
  filter(Theme == "FastStart") %>% 
  select(c(Session, attended)) %>% 
  arrange(desc(attended))

# make it look good
kable(
  fs_sessions,
  booktabs = T,
  linesep = "\\addlinespace",
  caption = "FastStart Sessions",
  align = c('lc'),
  col.names = c("Session", "Number of Attendees")) %>%
  column_spec (column = 1, width = "12cm") %>%
  kable_styling(latex_options = c("hold_position", "striped"))

```

\clearpage

```{r sessions and names by benchmark, include=TRUE}

# decide whether I want the full data set (df_all) or just the sessions
  # we've run to date (df_run)
df <- df_run

# how many sessions per theme
bench_sessions <- df %>%
  filter(Theme == "Benchmark") %>% 
  select(c(Session, attended)) %>% 
  arrange(desc(attended))

# make it look good
kable(
  bench_sessions,
  booktabs = T,
  linesep = "\\addlinespace",
  caption = "Benchmarking Your Research Career Sessions",
  align = c('lc'),
  col.names = c("Session", "Number of Attendees")) %>%
  column_spec (column = 1, width = "12cm") %>%
  kable_styling(latex_options = c("hold_position", "striped"))

```

```{r sessions and names by dev, include=TRUE}

# decide whether I want the full data set (df_all) or just the sessions
  # we've run to date (df_run)
df <- df_run

# how many sessions per theme
dev_sessions <- df %>%
  filter(Theme == "Development") %>% 
  select(c(Session, attended)) %>% 
  arrange(desc(attended))

# make it look good
kable(
  dev_sessions,
  booktabs = T,
  linesep = "\\addlinespace",
  caption = "Development Sessions",
  align = c('lc'),
  col.names = c("Session", "Number of Attendees")) %>%
  column_spec (column = 1, width = "12cm") %>%
  kable_styling(latex_options = c("hold_position", "striped"))

```

```{r sessions and names by prizes, include=TRUE}

# decide whether I want the full data set (df_all) or just the sessions
  # we've run to date (df_run)
df <- df_run

# how many sessions per theme
prize_sessions <- df %>%
  filter(Theme == "Prizes and Awards") %>% 
  select(c(Session, attended)) %>% 
  arrange(desc(attended))

# make it look good
kable(
  prize_sessions,
  booktabs = T,
  linesep = "\\addlinespace",
  caption = "Prizes and Awards Sessions",
  align = c('lc'),
  col.names = c("Session", "Number of Attendees")) %>%
  column_spec (column = 1, width = "12cm") %>%
  kable_styling(latex_options = c("hold_position", "striped"))

```








