---
title: "Researcher Training and Development Sessions for 2025"
subtitle: "As of Sept 30, 2025"
#author: "Jen Beaudry"
#date: "29/09/2025"
output: pdf_document
editor_options: 
  chunk_output_type: console
header-includes:
  - \usepackage{caption}
  - \usepackage{titling}
    \setlength{\droptitle}{-2cm} # removes some of the white space above title
  - \pretitle{\begin{center}
    \includegraphics[width=1.5in, height=1.5in]{flinders-university-horizontal-master.png}\LARGE\\} # adds logo
  - \posttitle{\end{center}}
  - \usepackage{fancyhdr}
  - \fancypagestyle{plain}{\pagestyle{fancy}} # sets the footer on page 1
  - \pagestyle{fancy} # sets the footer on page 2 and beyond
  - \fancyhf{} # clears existing header & footer
  - \renewcommand{\headrulewidth}{0pt} # removes the line from the header
  - \fancyfoot[L]{Researcher Training and Development 2025} # report name in footer
  - \fancyfoot[R]{\thepage} # page number in foooter
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE,
                      include = FALSE, 
                      eval = TRUE)

```

```{r library, eval=TRUE}


# Function to load or install packages
load_or_install <- function(packages) {
  for (package in packages) {
    if (!require(package, character.only = TRUE)) {
      install.packages(package, dependencies = TRUE)
      library(package, character.only = TRUE)
    }
  }
}

# Required packages 
packages <- c("here"
              , "tidyverse"
              , "kableExtra"
              , "readxl"
              , "janitor"
              , "rmarkdown"
              , "ggrepel" #for annotations in ggplot
              , "captioner"
              )

# Load or install the packages
load_or_install(packages)


```

```{r functions}

styler_pdf <- function(dat) {
  dat %>%
     kable_styling(full_width = F, 
                latex_options = c("striped", "HOLD_position"))
}

table_nums <- captioner(prefix = "Table")
fig_nums <- captioner(prefix = "Figure")

```


```{r load training data}

# load data from training spreadsheet (this is the complete number of attendees
  # & includes info about the theme)

df_sp <- read_xlsx(
  here::here("data",
             "2025_spreadsheet_data.xlsx"),
  sheet = '2025 Program',
  skip = 5, #start at the header row
  n_max = 94,  #last session was DP EOI
  .name_repair = "unique",
  trim_ws = TRUE)

# load data from ienrol (this contains names of Flinders attendees & includes college/portfolio info)

df_ienrol <- read_csv(here::here("data", "2025_ienrol_data.csv"), lazy = FALSE) %>% 
  clean_names()

# we also need to bring in the youtube views; see the spreadsheet in the youtube analytics folder
youtube <- "879"

```

```{r delete sessions that did not run, eval = FALSE}

# delete the sessions that were scheduled but not run [will need to compare to our training spreadsheet]
  # use the n_courses code in the next chunk to make it easy to figure out which sessions didn't run

df_remove1 <- df_ienrol %>% 
  filter(course_name == "ARC Discovery Projects EOI PItching Session for CHASS/CEPSW/CBGL" & event_num == "3")

list_df <- list(df_ienrol, df_remove1, df_remove2, df_remove3, df_remove4)

df_ienrol <- list_df %>%reduce(anti_join)

rm(df_remove1, df_remove2, df_remove3, df_remove4, list_df)

### [breadcrumb: at some point we will need to sort out how to collapse the courses in the ienrol dataframe, but for now we will do it in the n_courses in the next chunk]


```

```{r clean ienrol data}

# [breadcrumbs: when I have a chance I should move the preprocessing into a separate script]

df_ienrol <- df_ienrol %>%
  select (c(course_name, event_num, first_name, last_name, fan, department, job_status, status)) 

# turn them into factors

cols <- c("course_name",
          "event_num",
             "department",
             "job_status",
             "status")

# recode status and department

df_ienrol <- df_ienrol %>% 
  dplyr::mutate(across(all_of(cols), ~factor(.))) %>% 
  dplyr::mutate(attendance_status = case_when (status == "attended" ~ "Attended", 
                                        status == "didnotattend" ~ "Did not attend")) %>% 
  dplyr::mutate(portfolio = case_when (grepl("Research", department) ~ "Portfolio of the Deputy Vice-Chancellor (Research)", #recode RDS as DVC(R)
                                    !grepl("College of", department) ~ "Other portfolios",
                                    department == "Other" ~ "Other",
                                    department == "Unknown" ~ "Other", 
                                    TRUE ~ as.factor(as.character(department))))


# summarise the data based on how many courses were held and how many folks attended each of the sessions

n_courses_all <- df_ienrol %>% 
#  filter(attendance_status == "Attended") %>% 
  count(course_name, event_num)

n_courses <- df_ienrol %>% 
  filter(attendance_status == "Attended") %>% 
  count(course_name, event_num)

# any course with zero attendees will not show up in n_courses. We need to manually add them back in. 
  # 2025: we don't seem to have any courses that were not included, so skip this for now. 

# add_df <- list(course_name = "Research Ethics & Biosafety Applications Hands-on Workshop", 
#           event_num = "3", 
#           n = "0") %>% as_tibble %>% 
#   mutate(
#     course_name = as.factor(course_name), 
#     event_num = as.factor(event_num), 
#     n = as.integer(n))

# n_courses <- full_join(n_courses,add_df) 

# rm(add_df)


# this number of attendees will differ from the T&D spreadsheet because we have had attendees that are not in iEnrol

n_attendees_ienrol <- df_ienrol %>%
  filter(attendance_status == "Attended") %>% 
  count(fan, course_name, event_num)

# unique attendees 
n_unique_attendees_ienrol <- n_distinct(n_attendees_ienrol$fan)


# all attendees broken down by College

df_portfolios <- df_ienrol %>% 
  filter (portfolio == "Other portfolios") %>% 
  count(department) %>% 
  arrange(-n)

n_portfolios <- unique(df_portfolios$department)

# Attendance status

attended <- df_ienrol %>% filter(attendance_status == "Attended")
not_attended <- df_ienrol %>% filter(attendance_status == "Did not attend")

```

<!-- I use the following code to find the issues. But we don't need to run them with the full report. -->
<!-- Number of courses shown in iEnrol, with registrations = `r nrow(n_courses)`. Compare this to the number of rows in df_sp. -->


```{r show all ienrol courses with registrations, include = TRUE, eval = FALSE}

# make it look good
kable(n_courses_all, 
      booktabs = T,
      align = c('lcc'), 
      caption = "Sessions recorded in iEnrol for 2025; N shows all registrations, not only attendees",
      linesep = "\\addlinespace") %>% 
  kable_styling(latex_options = c("hold_position", "striped")) 

```

<!-- Number of courses shown in iEnrol, with attendees = `r nrow(n_courses)` -->

```{r show all ienrol courses with attendees, include = TRUE, eval = FALSE}

# make it look good
kable(n_courses, 
      booktabs = T,
      align = c('lcc'), 
      caption = "Sessions recorded in iEnrol for 2025; N shows only attendees",
      linesep = "\\addlinespace") %>% 
  kable_styling(latex_options = c("hold_position", "striped")) 

# compare all ienrol courses with registrations to courses with attendees
n_compare <- anti_join(n_courses_all, n_courses, by = c("course_name", "event_num"))

# this is text that didn't work for some reason. Use it when you're first cleaning the data
# Number of courses shown in iEnrol, with registrations = `r nrow(n_courses_all)`

```


```{r compare all ienrol courses with registrations to courses with attendees, incl = FALSE, eval = FALSE}

# make it look good
kable(n_compare, 
      booktabs = T,
      align = c('lcc'), 
      caption = "Sessions that are in the ienrol registrations without attendees",
      linesep = "\\addlinespace") %>% 
  kable_styling(latex_options = c("hold_position", "striped")) 

```


```{r compare all ienrol courses with courses in our spreadsheet, incl = FALSE, eval = FALSE}

# 2025: we have more sessions in our spreadsheet than in ienrol, so now I have to figure out which ones...

n_courses_2 <- n_courses %>% 
  rename (Session = "course_name") %>% 
  mutate (data_source = "iEnrol")

df_sp_2 <- df_sp %>% 
    mutate (data_source = "spreadsheet")

# compare the two tibbles & see what doesn't match. Difficult to code because names are slightly different
ienrol_vs_sp <- anti_join(n_courses_2, df_sp, by = "Session")
sp_vs_ienrol <- anti_join(df_sp, n_courses_2, by = "Session")

# [breadcrumb] 2025: two sessions missing from ienrol that need to be added in - FNRC August & Indigenous Research Showcase

rm(n_courses_2, df_sp_2, ienrol_vs_sp, sp_vs_ienrol)

```


```{r clean spreadsheet data}

df_sp <- df_sp %>% 
   dplyr::rename("Attended" = "No. attended") %>%
     dplyr::rename("Attended_in_person" = "No. In person attendees") %>%
     dplyr::rename("Attended_online" = "No. Online attendees") %>%
    select(c(Theme, Event, Attended, Session, Attended_in_person, Attended_online)) %>% 
  mutate("Event" = as.factor(Event))

# this number will differ from the T&D spreadsheet because we have had attendees that are not in iEnrol

n_attended_sp <- sum(df_sp$Attended)

# figure out how many sessions were held face-to-face vs. online & how many folks attended in person or online for hybrid events
n_event_sp <- df_sp %>% 
  filter(Event == "E")

# rename the collective theme in the spreadsheet 
  
df_sp [df_sp == "FNRC"] <- "First Nations Researchers Collective"
df_sp [df_sp == "Commerce"] <- "Post-award, Intellectual Property, and Commercialisation"

```

<!-- Number of courses shown in spreadsheet = `r nrow(df_sp)` -->

```{r show all spreadsheet courses, include = TRUE, eval = FALSE}

#combine sessions & attendees per theme
simple_df_sp <- df_sp %>% 
  select (c(Session, Attended)) %>% 
  dplyr::arrange(Session) # put it in alphabetical order


# make it look good
kable(simple_df_sp, 
      booktabs = T,
      align = c('lc'), 
      caption = "Sessions recorded in spreadsheet for 2025",
      linesep = "\\addlinespace") %>% 
  kable_styling(latex_options = c("hold_position", "striped")) 

```


```{r captions, eval = TRUE}

# use these to provide the captions and numbers for the figures 
# use kable captions to provide the captions for the Tables, but use the captioner package
  # to be able to reference the tables within the text

fig_nums(name = "college_attendees", 
         caption = "Number of Attendees in Training & Development Sessions (2025)")

fig_nums(name = "college_unique_attendees", 
         caption = "Number of Unique Attendees in Training & Development Sessions (2025)")

fig_nums(name = "job_status_attendees", 
         caption = "Number of Attendees in Training & Development Sessions (2025)")

fig_nums(name = "job_status_unique_attendees", 
         caption = "Number of Unique Attendees in Training & Development Sessions (2025)")

table_nums(name = "theme_overview", 
          caption = "Training and Development Summary for 2025")

table_nums(name = "sessions_by_theme", 
          caption = "Training and Development Sessions by Theme for 2025")

```

## Summary

In 2025, the Training, Development and Communication team in Research
Development and Support have offered `r nrow(n_courses)` information
sessions and development workshops to researchers and research support
staff at Flinders University. 

From the Flinders community, `r nrow(n_attendees_ienrol)` people attended the 
research training and development sessions thus far in 2025. Our actual attendance numbers 
are larger (*n* = `r sum(df_sp$Attended)`) because we allowed 
external researchers to join select sessions (e.g., Open Research sessions, 
the inaugural NADOIC Indigenous Research Showcase, etc.). 
Of the `r nrow(n_attendees_ienrol)` attendees from Flinders, 
`r n_unique_attendees_ienrol` were unique attendees, demonstrating
that a large number of people from the Flinders research community are engaging in
our research training and development program.

The number of attendees at our sessions varied from `r min(n_courses$n)` in three sessions
(i.e., an animal ethics information session, an Intellectual Property workshop for the 
Colleges of HASS, EPSW, and BGL, and a bespoke DECRA Development Workshop for a selected
group of applicants) to `r max(n_courses$n)` in our first session on Microsoft 
CoPilot and AI for research. The mean number of attendees at 
our sessions was `r round(mean(n_courses$n),0)` with a median of 
`r round(median(n_courses$n),0)`.

In this report, we first break down our enrolments by College and Portfolio. We
then explore the topics of the sessions in more detail. We provide an overview
of the number of sessions and number of attendees by theme, and then
report the number of attendees in each session organised by theme.

## Number of Attendees by College and Portfolio

`r fig_nums(name = "college_attendees", display = "cite")` illustrates how many 
people attended these sessions across the Colleges and Portfolios. By far, the 
largest number of attendees were in the College of Medicine and Public Health, 
which is representative of the large number of researchers in that College.

Most of the professional staff who attended our training and development sessions 
were from the Portfolio of the Deputy Vice-Chancellor (Research). We collapsed all
other portfolios in the University into a single "Other portfolios" category
because of the large number of portfolios that our attendees represent
(including Library; Learning and Teaching Innovation; Information and Digital Services; 
Chief of Staff Portfolio; and Governance, Legal and Risk; as well as people who are not
aligned with any portfolio in the iEnrol system).

Overall, across all Colleges and Portfolios, the average attendance rate for
2025 was `r round(((nrow(attended)/(nrow(attended) + nrow(not_attended)))*100), 0)`%. 
This is slightly lower than the attendance rate from 2024 (65%). 

`r fig_nums(name = "college_unique_attendees", display = "cite")` illustrates the unique
number of attendees across the Colleges and Portfolios. The College of Medicine
and Public Health also had the most unique attendees.


```{r plot the ienrol attendance with rate, eval=FALSE, fig.width = 15, fig.height = 9}

#combine sessions & attendees & attendance rate per portfolio
df_grouped <- df_ienrol %>%
  count(portfolio, attendance_status) %>%
    group_by(portfolio) %>%
    mutate(att_pct = (n/sum(n)) *100) %>%
    mutate(enrol = sum(n))


# add in the attendance label here & rearrange it so it matches the data (which will be reordered in ggplot)
df_label <- df_grouped %>%
   dplyr::mutate(
  perc_label = paste0(sprintf("\n\nAttendance rate = %1.1f", att_pct), "%"),
  port_perc_label = paste(portfolio, perc_label)) %>%
  filter(attendance_status == "Attended") %>%
  arrange(n)


#use this to reorder the attendance factor within the ggplot code
attend <- c("Did not attend", "Attended")


# plot it [this has attendance & non-attendance numbers & attendance rates in the names for the portfolios]
ggplot(df_grouped, aes(
  x = reorder(portfolio, n),
  fill = factor(attendance_status, levels = attend),
  y = n
)) +
  geom_bar(stat = "identity", colour = "black") +
  geom_text(aes(y = n,
                x = portfolio,
                label = n),
            position = position_stack(vjust = 0.5),
            size = 6) +
  coord_flip() +
  labs (title = "Attendance by College and Portfolios (2025)",
        x = element_blank(),
        y = "Number of enrolments") +
  theme_classic() +
  theme(
    legend.title = element_blank(),
    legend.position = c(0.8, 0.2),
    title = element_text(size = 14, family="sans"),
    legend.text = element_text(size = 14, family="sans"),
    axis.text = element_text(size = 14, family ="sans"),
    axis.title = element_text(size = 14, family = "sans")
    ) +
  scale_fill_manual(
    values = c("#bfbfbf", "#90b8da"),
    labels = c("Did not attend", "Attended"),
    guide = guide_legend (reverse = TRUE)
  ) +
  scale_x_discrete(
    labels = df_label$port_perc_label)


#ggsave(plot = last_plot(),filename = here::here("figures", "2025 attendance rates by portfolio.png"),
#       width = 15, height = 9, dpi = 300)

```

\newpage
`r fig_nums(name = "college_attendees")`

```{r plot the ienrol attendance, include = TRUE, eval=TRUE, fig.width = 15, fig.height = 9}

# this is the good one

# count attendees rate per portfolio
df_attend <- df_ienrol %>%
  filter(attendance_status == "Attended") %>%
  count(portfolio)


# plot it [this has attendance numbers by the portfolios]
ggplot(df_attend, aes(
  x = reorder(portfolio, n),
  y = n
)) +
  geom_bar(stat = "identity", colour = "black", fill = "#90b8da") +
  geom_text(aes(y = n,
                x = portfolio,
                label = n),
            position = position_stack(vjust = 0.5),
            size = 6) +
  coord_flip() +
  labs (#title = "Number of Attendees in Training & Development Sessions (2025)", # included in caption
        x = element_blank(),
        y = "Number of attendees") +
  theme_classic() +
  theme(
    title = element_text(size = 14, family="sans"),
    legend.text = element_text(size = 14, family="sans"),
    axis.text = element_text(size = 14, family ="sans"),
    axis.title = element_text(size = 14, family = "sans")
    ) +
  scale_fill_manual(
    values = "#90b8da"
  )
 # scale_x_discrete(
 #   labels = df_label$port_perc_label)


ggsave(plot = last_plot(),filename = here::here("figures", "2025 attendance by portfolio.png"),
       width = 15, height = 9, dpi = 300)

```

\vskip 0.3in

`r fig_nums(name = "college_unique_attendees")`

```{r plot the ienrol attendance for unique attendees, include = TRUE, eval=TRUE, fig.width = 15, fig.height = 9}

# count unique attendees per portfolio
df_attend_unique <- df_ienrol %>%
  filter(attendance_status == "Attended") %>%
  distinct(fan, attendance_status, portfolio) %>%
  count(portfolio)


# plot it [this has unique attendance numbers by the portfolios]
ggplot(df_attend_unique, aes(
  x = reorder(portfolio, n),
  y = n
)) +
  geom_bar(stat = "identity", colour = "black", fill = "#90b8da") +
  geom_text(aes(y = n,
                x = portfolio,
                label = n),
            position = position_stack(vjust = 0.5),
            size = 6) +
  coord_flip() +
  labs (#title = "Number of Unique Attendees in Training & Development Sessions (2025)", # included in caption
        x = element_blank(),
        y = "Number of unique attendees") +
  theme_classic() +
  theme(
    title = element_text(size = 14, family="sans"),
    legend.text = element_text(size = 14, family="sans"),
    axis.text = element_text(size = 14, family ="sans"),
    axis.title = element_text(size = 14, family = "sans")
    ) +
  scale_fill_manual(
    values = "#90b8da"
  )
 # scale_x_discrete(
 #   labels = df_label$port_perc_label)


ggsave(plot = last_plot(),filename = here::here("figures", "2025 unique attendance by portfolio.png"),
       width = 15, height = 9, dpi = 300)

```


## Number of Attendees According to their Role

```{r ienrol attendance by role, eval=TRUE}

# count attendees rate by role
df_attend <- df_ienrol %>%
  filter(attendance_status == "Attended") %>% 
  count(job_status)

# count unique attendees per portfolio
df_attend_unique_role <- df_ienrol %>%
  filter(attendance_status == "Attended") %>%
  distinct(fan, attendance_status, job_status) %>%
  count(job_status)

```


`r fig_nums(name = "job_status_attendees", display = "cite")` illustrates the
number of attendees according to their role, as reported in the iEnrol system.
The majority of attendees were academic staff members
(`r round(df_attend %>% filter(job_status=="Academic") %>% select(n)/sum(df_attend$n)*100 ,0)`%),
followed by professional staff members (`r round(df_attend %>% filter(job_status=="Professional") %>% select(n)/sum(df_attend$n)*100 ,0)`%).
Only `r round(df_attend %>% filter(job_status=="Student") %>% select(n)/sum(df_attend$n)*100 ,0)`% 
of attendees at our sessions were students;
the iEnrol system does not differentiate between postgraduate and undergraduate
students, so we cannot further break down this category. This number likely
underestimates the number of students who attended our sessions because
some students are also staff members. 

An analysis of the unique attendees (not shown here), indicates that the largest cohort of unique 
attendees were academic staff members.

\vskip 0.3in

`r fig_nums(name = "job_status_attendees")`

```{r plot the ienrol attendance by role, include = TRUE, eval=TRUE, fig.width = 15, fig.height = 9}

# count attendees rate by role
df_attend <- df_ienrol %>%
  filter(attendance_status == "Attended") %>%
  count(job_status)

# need to note the threshold for the labels so only the smaller ones are repelled.
threshold <- 100

# plot it [this has attendance numbers by their role, as reported in ienrol]
ggplot(df_attend, aes(
  x = reorder(job_status, n),
  y = n
)) +
  geom_bar(stat = "identity", colour = "black", fill = "#90b8da") +
  geom_text(aes(y = n,
                x = job_status,
                label = ifelse(n>threshold, n, "")),
            position = position_stack(vjust = 0.5),
            size = 6) +
  geom_text_repel(aes(y = n,
                      x = job_status,
                      label = ifelse(n<threshold, n, "")), 
                  box.padding = 0.25,
                  size = 6) +
  coord_flip() +
  labs (#title = "Number of Attendees in Training & Development Sessions (2025)", # included in caption
        x = element_blank(),
        y = "Number of attendees") +
  theme_classic() +
  theme(
    title = element_text(size = 14, family="sans"),
    legend.text = element_text(size = 14, family="sans"),
    axis.text = element_text(size = 14, family ="sans"),
    axis.title = element_text(size = 14, family = "sans")
    ) +
  scale_fill_manual(
    values = "#90b8da"
  )
 # scale_x_discrete(
 #   labels = df_label$port_perc_label)


# ggsave(plot = last_plot(),filename = here::here("figures", "2025 attendance by role.png"),
#        width = 15, height = 9, dpi = 300)

```

\newpage


```{r plot the ienrol attendance for unique attendees by role, include = TRUE, eval=FALSE, fig.width = 15, fig.height = 9}

# count unique attendees per portfolio
df_attend_unique <- df_ienrol %>%
  filter(attendance_status == "Attended") %>%
  distinct(fan, attendance_status, job_status) %>%
  count(job_status)


# plot it [this has unique attendance numbers by the portfolios]
ggplot(df_attend_unique, aes(
  x = reorder(job_status, n),
  y = n
)) +
  geom_bar(stat = "identity", colour = "black", fill = "#90b8da") +
  geom_text(aes(y = n,
                x = job_status,
                label = n),
            position = position_stack(vjust = 0.5),
            size = 6) +
  coord_flip() +
  labs (#title = "Number of Unique Attendees in Training & Development Sessions (2025)", # included in caption
        x = element_blank(),
        y = "Number of unique attendees") +
  theme_classic() +
  theme(
    title = element_text(size = 14, family="sans"),
    legend.text = element_text(size = 14, family="sans"),
    axis.text = element_text(size = 14, family ="sans"),
    axis.title = element_text(size = 14, family = "sans")
    ) +
  scale_fill_manual(
    values = "#90b8da"
  )
 # scale_x_discrete(
 #   labels = df_label$port_perc_label)


ggsave(plot = last_plot(),filename = here::here("figures", "2025 unique attendance by portfolio.png"),
       width = 15, height = 9, dpi = 300)

```



\vskip 0.3in

## Overview of Research Training and Development Topics

Next, we explore the topics of the sessions in more detail.

`r table_nums(name = "theme_overview", display = "cite")` shows the number
of sessions and attendees by theme. The largest number of sessions offered was in the
'Research Funding' theme, demonstrating Flinders University's commitment
to support and develop researchers so they can attract external research funding. The fact that this theme
also had the largest number of attendees is evidence that the research community
values these training and development opportunities.

The numbers presented in the following tables reflect the total number of attendees
(*n* = `r n_attended_sp`), most of whom are from Flinders
(*n* = `r nrow(n_attendees_ienrol)`).

### Delivery Modality

Of the `r nrow(n_courses)` sessions that we offered in 2025, `r nrow(n_event_sp)` 
(`r round((nrow(n_event_sp))/nrow(n_courses)*100, 0)`%)
were held face-to-face, with a hybrid option available whenever possible for those who 
could not attend in person. Unfortunately, it was not possible to offer a hybrid 
option for a few sessions, such as interactive workshops. We will continue to explore 
how to connect with and support our Rural, Regional and Remote colleagues in the future. 
The remainder of the sessions 
(*n* = ;`r round(((nrow(n_courses)-nrow(n_event_sp))/(nrow(n_courses))*100),0)`%) 
were offered online through synchronous delivery. 

Overall, across all Colleges and Portfolios, the average attendance rate for
2025 was `r round(((nrow(attended)/(nrow(attended) + nrow(not_attended)))*100), 0)`%. 
This is slightly lower than the attendance rate from 2024 (65%). 

To better understand our research community's preference for online versus in-person
events, in 2025, we recorded the number of attendees at our hybrid sessions who 
attended in person (`r sum(n_event_sp$Attended_in_person)`; 
(`r round((sum(n_event_sp$Attended_in_person))/sum(n_event_sp$Attended)*100, 0)`%) 
or online (`r sum(n_event_sp$Attended_online)`; 
(`r round((sum(n_event_sp$Attended_online))/sum(n_event_sp$Attended)*100, 0)`%) . 
Although it is likely that the Flinders' 
research community prefer to meet face-to-face when possible, this in-person 
preference might be inflated by our team's decision to require people to request an 
online link for in-person sessions rather than providing it by default. 


\vskip 0.3in

```{r theme overview, include = TRUE, eval = TRUE}

#combine sessions & attendees per theme
theme_overview <- df_sp %>%
  group_by(Theme) %>%
  summarise(`Number of Sessions` = n(),
            `Number of Attendees` = sum(Attended)) %>%
  arrange (desc(`Number of Attendees`)) %>%
    adorn_totals("row")

# make it look good
kable(theme_overview,
      booktabs = T,
      align = c('lcc'),
      caption = "Training and Development Summary for 2025",
      linesep = "\\addlinespace") %>%
  kable_styling(latex_options = c("hold_position", "striped"))

```


```{r fund and apply 2025 by team, include = TRUE, eval = FALSE}

# [breadcrumb: This is very useful for working with the grants team, but does not need to be
  # part of this report. Pull out into its own Rmd.]

fund_23 <- df %>%
  filter(Theme == "Fund and Apply") %>%
  select (Attended, Session) %>%
  relocate (Attended, .after = Session) %>%
      mutate ("Number" = 1:n()) %>%
    relocate (Number)

fund_team_23 <- fund_23 %>%
  mutate(Team = case_when(
    grepl("NHMRC", Session) ~ "NHMRC",
    grepl("ARC", Session) ~ "ARC",
    grepl("MRFF", Session) ~ "MRFF",
    TRUE ~ as.character("Other"))
  ) %>%
  select (-Number) %>%
  arrange(Team, desc(Attended)) %>%
        mutate ("Number" = 1:n()) %>%
    relocate (Number)


total_fund_team_23 <- sum(fund_team_23$Attended)

knitr::kable (
 fund_team_23 [, 1:3], # select only the names and levels columns
  booktabs = T,
   linesep = "",
  col.names = c("Session Number", "Session Name", "Number of Attendees"),
  caption =
    sprintf("Fund and Apply sessions in 2025 (n = %d)",
            total_fund_team_23),
  align = 'clc',
  longtable = T #break the table over multiple pages
  ) %>%
   column_spec(1, width = "0.5in") %>%
   column_spec(2, width = "5in") %>%
  column_spec(3, width = "0.75in") %>%
  pack_rows (index = table(fund_team_23$Team)) %>%
  kable_styling(full_width = F,
                latex_options = c("repeat_header", "hold_position", "striped"))

```

\newpage

`r table_nums(name = "sessions_by_theme", display = "cite")` provides
additional detail about the specific sessions that we ran within each of the
training and development themes.

\vskip 0.3in

```{r sessions and attendees by theme, include = TRUE, eval=TRUE}

# how many sessions per theme
theme_sessions <- df_sp %>%
  group_by(Theme) %>%
  select(c(Theme, Session, Attended)) %>%
  arrange(Theme, Session) %>%
  mutate(Theme = as.factor(Theme))

# make it look good
kable(theme_sessions [, 2:3],
  booktabs = T,
  linesep = "\\addlinespace",
  col.names = c("Sessions by Themes", "Number of Attendees"),
  caption =
    sprintf("Training and Development Sessions for 2025 (n = %d)",
            n_attended_sp),
  align = 'lr',
  longtable = T #break the table over multiple pages
  ) %>%
  column_spec(1, width = "5in") %>%
  column_spec(2, width = "1in") %>%
  pack_rows (index = table(theme_sessions$Theme),
               latex_gap_space = "0.4em",) %>%
    kable_styling(
    full_width = F,
    latex_options = c("repeat_header", "hold_position", "striped")
  )

```



```{r unique sessions by theme, include = FALSE, eval=FALSE}

# to answer P&C's question of how many unique courses we offer

# how many sessions per theme -- just a quick and dirty report. Copy and paste into excel.

print(unique(df_sp$Session))

```


\vskip 0.4in

If you have any questions or suggestions for additional researcher training and development
sessions, please contact Dr Jen Beaudry (Manager, Researcher Training, Development
and Communication) in Research Development and Support.
