---
title: "Researcher Training and Development Sessions for 2023"
#subtitle: "Enrolment and Attendance Statistics for EPSW"
#author: "Jen Beaudry"
#date: "19/10/2023"
output: pdf_document
editor_options: 
  chunk_output_type: console
params: 
  portfolio: "College of Education, Psychology and Social Work"
  printcode: FALSE 
header-includes:
  - \usepackage{caption}
  - \usepackage{titling}
    \setlength{\droptitle}{-2cm} # removes some of the white space above title
  - \pretitle{\begin{center}
    \includegraphics[width=1.5in, height=1.5in]{flinders-university-horizontal-master.png}\LARGE\\} # adds logo
  - \posttitle{\end{center}}
  - \usepackage{fancyhdr}
  - \fancypagestyle{plain}{\pagestyle{fancy}} # sets the footer on page 1
  - \pagestyle{fancy} # sets the footer on page 2 and beyond
  - \fancyhf{} # clears existing header & footer
  - \renewcommand{\headrulewidth}{0pt} # removes the line from the header
  - \fancyfoot[L]{Jen Beaudry} # my name in footer
  - \fancyfoot[R]{\thepage} # page number in foooter
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE,
                      include = FALSE, 
                      eval = TRUE)

```

```{r library, eval=TRUE}

library(here)
library(tidyverse)
library(kableExtra)
library(readxl)
library(janitor)
library(rmarkdown)
library(ggrepel) #for annotations in ggplot
library(captioner)

```

```{r functions}

styler_pdf <- function(dat) {
  dat %>%
     kable_styling(full_width = F, 
                latex_options = c("striped", "HOLD_position"))
}

table_nums <- captioner(prefix = "Table")
fig_nums <- captioner(prefix = "Figure")

```


```{r load training data}

# load data from training spreadsheet (this is the complete number of attendees
  # & includes info about the theme)

df_sp <- read_xlsx(
  here::here("data",
             "2023_training_data.xlsx"),
  sheet = '2023 Program',
  skip = 7,
  n_max = 102,  #last session Cruxes on Dec 12
  .name_repair = "unique",
  trim_ws = TRUE)

# load data from ienrol (this contains names of Flinders attendees & includes college/portfolio info)

df_ienrol <- read_csv(here::here("data", "2023_ienrol_data.csv"), lazy = FALSE) %>% 
  clean_names()

```

```{r delete sessions that did not run}

# delete the sessions that were scheduled but not run [will need to compare to our training spreadsheet]
  # use the n_courses code in the next chunk to make it easy to figure out which sessions didn't run

df_remove1 <- df_ienrol %>% 
  filter(course_name == "Open Research Practices" & event_num == "2")

df_remove2 <- df_ienrol %>% 
  filter(course_name == "The Strategic Researcher") 

df_remove3 <- df_ienrol %>% 
  filter(course_name == "Foreign Interactions Information for Researchers") 

df_remove4 <- df_ienrol %>% 
  filter(course_name == "ARC DECRA Development Session")

df_remove5 <- df_ienrol %>% 
  filter(course_name == "NHMRC Investigator Grants Information Session" & event_num == "1")

df_remove_a <- full_join(df_remove1, df_remove2)
df_remove_a <- full_join(df_remove_a, df_remove3)
df_remove_a <- full_join(df_remove_a, df_remove4)
df_remove_a <- full_join(df_remove_a, df_remove5)

df_ienrol <- anti_join (df_ienrol, df_remove_a)

rm(df_remove1, df_remove2, df_remove3, df_remove4, df_remove5, df_remove_a)

```

```{r clean ienrol data}

# [breadcrumbs: when I have a chance I should move the preprocessing into a separate script]

df_ienrol <- df_ienrol %>%
  select (c(course_name, event_num, first_name, last_name, fan, department, job_status, status)) 

# turn them into factors

cols <- c("course_name",
          "event_num",
             "department",
             "job_status",
             "status")

# recode status and department

df_ienrol <- df_ienrol %>% 
  dplyr::mutate(across(all_of(cols), ~factor(.))) %>% 
  dplyr::mutate(attendance_status = case_when (status == "attended" ~ "Attended", 
                                        status == "didnotattend" ~ "Did not attend")) %>% 
  dplyr::mutate(portfolio = factor(case_when (grepl("Research", department) ~ "Portfolio of the Deputy Vice-Chancellor (Research)", #recode RDS as DVC(R)
                                    !grepl("College of", department) ~ "Other portfolios",
                                    department == "Other" ~ "Other",
                                    department == "Unknown" ~ "Other", 
                                    TRUE ~ as.factor(as.character(department)))))


# summarise the data based on how many courses were held and how many folks attended each of the sessions

n_courses <- df_ienrol %>% 
  filter(attendance_status == "Attended") %>% 
  count(course_name, event_num)


# this number will differ from the T&D spreadsheet because we have had attendees that are not in iEnrol

df_ienrol_att <- df_ienrol %>%
  filter(attendance_status == "Attended")

# unique attendees 
n_unique_attendees_ienrol <- n_distinct(df_ienrol_att$fan)


# all attendees broken down by College

df_portfolios <- df_ienrol_att %>% 
  filter (portfolio == "Other portfolios") %>% 
  count(department) %>% 
  arrange(-n)

n_portfolios <- unique(df_portfolios$department)

# Attendance status

attended <- df_ienrol %>% filter(attendance_status == "Attended")
not_attended <- df_ienrol %>% filter(attendance_status == "Did not attend")

# [breadcrumb: inline text with college details]
# Within the College of Education, Psychology and Social Work, 
# `r sum(df_ienrol_att$portfolio=="College of Education, Psychology and Social Work")`

```

```{r clean spreadsheet data}

df_sp <- df_sp %>% 
  select(c(Theme, `No. attended`, Session)) %>% 
    dplyr::rename("Attended" = "No. attended")


# this number will differ from the T&D spreadsheet because we have had attendees that are not in iEnrol

n_attended_sp <- sum(df_sp$Attended)

```

```{r captions}

# use these to provide the captions and numbers for the figures 
# use kable captions to provide the captions for the Tables, but use the captioner package
  # to be able to reference the tables within the text

fig_nums(name = "college_attendees", 
         caption = "Number of Attendees in Training & Development Sessions (2023)")

fig_nums(name = "college_unique_attendees", 
         caption = "Number of Unique Attendees in Training & Development Sessions (2023)")

table_nums(name = "theme_overview", 
          caption = "Training and Development Summary for 2023")

table_nums(name = "sessions_by_theme", 
          caption = "Training and Development Sessions by Theme for 2023")

```

## Summary 

In 2023, the Training, Development and Communication team in Research
Development and Support have offered `r nrow(n_courses)` information 
sessions and development workshops to researchers and research support
staff at Flinders University. 

From the Flinders community, `r nrow(df_ienrol_att)` people attended the research training and 
development sessions in 2023. Our actual attendance numbers for the year are larger (*n* = `r sum(df_sp$Attended)`)
because we allowed external researchers to join select sessions (e.g., Open 
Research sessions; ARC Outreach sessions, etc.). Of the Flinders `r nrow(df_ienrol_att)` 
attendees, `r n_unique_attendees_ienrol` were unique attendees, demonstrating 
that a large number of people from the Flinders research community are engaging in 
our research training and development program. 

The number of attendees at our sessions varied from `r min(n_courses$n)` in a 
hands-on ethics workshop to `r max(n_courses$n)` in a research grant writing workshop. 
The mean number of attendees at our sessions was `r round(mean(n_courses$n),0)` 
with a median of `r round(median(n_courses$n),0)`. 

In this report, we first break down our enrolments by College and portfolio. We 
then explore the topics of the sessions in more detail. We provide an overview
of the number of sessions and number of attendees by theme, and then 
report the number of attendees in each session organised by theme.

## Number of Attendees by College and Portfolio

`r fig_nums(name = "college_attendees", display = "cite")` illustrates how many people 
attended these sessions across the Colleges and portfolios. By far, the largest 
number of attendees were in the College of Medicine and Public Health, which is 
representative of the large number of researchers in that College. 

Most of the professional staff who attended our training and development sessions were 
from the Portfolio of the Deputy Vice-Chancellor (Research). We collapsed all 
other portfolios in the University into a single "Other portfolios" category 
because of the large number of portfolios that our registrants represent 
(including Library, Information and Digital Services, as well as people who are not 
aligned with any portfolio in the iEnrol system). 

Overall, across all Colleges and 
portfolios, the average attendance rate for 
2023 was `r round(((nrow(attended)/(nrow(attended) + nrow(not_attended)))*100), 2)`%.

`r fig_nums(name = "college_unique_attendees", display = "cite")` illustrates the unique 
number of attendees across the Colleges and portfolios. The College of Medicine 
and Public Health also had the most unique attendees. 


```{r plot the ienrol attendance with rate, eval=FALSE, fig.width = 15, fig.height = 9}

#combine sessions & attendees & attendance rate per portfolio
df_grouped <- df_ienrol %>%
  count(portfolio, attendance_status) %>% 
    group_by(portfolio) %>% 
    mutate(att_pct = (n/sum(n)) *100) %>%
    mutate(enrol = sum(n))


# add in the attendance label here & rearrange it so it matches the data (which will be reordered in ggplot)
df_label <- df_grouped %>% 
   dplyr::mutate(
  perc_label = paste0(sprintf("\n\nAttendance rate = %1.1f", att_pct), "%"), 
  port_perc_label = paste(portfolio, perc_label)) %>% 
  filter(attendance_status == "Attended") %>% 
  arrange(n)


#use this to reorder the attendance factor within the ggplot code 
attend <- c("Did not attend", "Attended")


# plot it [this has attendance & non-attendance numbers & attendance rates in the names for the portfolios]
ggplot(df_grouped, aes(
  x = reorder(portfolio, n),
  fill = factor(attendance_status, levels = attend),
  y = n
)) +
  geom_bar(stat = "identity", colour = "black") +
  geom_text(aes(y = n,
                x = portfolio,
                label = n),
            position = position_stack(vjust = 0.5),
            size = 6) +
  coord_flip() +
  labs (title = "Attendance by College and Portfolios (2023)", 
        x = element_blank(),
        y = "Number of enrolments") +
  theme_classic() +
  theme(
    legend.title = element_blank(),
    legend.position = c(0.8, 0.2),
    title = element_text(size = 14, family="sans"),
    legend.text = element_text(size = 14, family="sans"),
    axis.text = element_text(size = 14, family ="sans"), 
    axis.title = element_text(size = 14, family = "sans") 
    ) +
  scale_fill_manual(
    values = c("#bfbfbf", "#90b8da"),
    labels = c("Did not attend", "Attended"),
    guide = guide_legend (reverse = TRUE)
  ) +
  scale_x_discrete(
    labels = df_label$port_perc_label) 


#ggsave(plot = last_plot(),filename = here::here("figures", "2023 attendance rates by portfolio.png"),
#       width = 15, height = 9, dpi = 300)

```

\newpage
`r fig_nums(name = "college_attendees")`

```{r plot the ienrol attendance, include = TRUE, eval=TRUE, fig.width = 15, fig.height = 9}

# count attendees rate per portfolio
df_attend <- df_ienrol %>%
  filter(attendance_status == "Attended") %>% 
  count(portfolio)


# plot it [this has attendance numbers by the portfolios]
ggplot(df_attend, aes(
  x = reorder(portfolio, n),
  y = n
)) +
  geom_bar(stat = "identity", colour = "black", fill = "#90b8da") +
  geom_text(aes(y = n,
                x = portfolio,
                label = n),
            position = position_stack(vjust = 0.5),
            size = 6) +
  coord_flip() +
  labs (#title = "Number of Attendees in Training & Development Sessions (2023)", # included in caption
        x = element_blank(),
        y = "Number of attendees") +
  theme_classic() +
  theme(
    title = element_text(size = 14, family="sans"),
    legend.text = element_text(size = 14, family="sans"),
    axis.text = element_text(size = 14, family ="sans"), 
    axis.title = element_text(size = 14, family = "sans") 
    ) +
  scale_fill_manual(
    values = "#90b8da"
  ) 
 # scale_x_discrete(
 #   labels = df_label$port_perc_label) 


ggsave(plot = last_plot(),filename = here::here("figures", "2023 attendance by portfolio.png"),
       width = 15, height = 9, dpi = 300)

```

\vskip 0.3in

`r fig_nums(name = "college_unique_attendees")`

```{r plot the ienrol attendance for unique attendees, include = TRUE, eval=TRUE, fig.width = 15, fig.height = 9}

# count attendees rate per portfolio
df_attend_unique <- df_ienrol %>%
  filter(attendance_status == "Attended") %>% 
  distinct(fan, attendance_status, portfolio) %>% 
  count(portfolio)


# plot it [this has unique attendance numbers by the portfolios]
ggplot(df_attend_unique, aes(
  x = reorder(portfolio, n),
  y = n
)) +
  geom_bar(stat = "identity", colour = "black", fill = "#90b8da") +
  geom_text(aes(y = n,
                x = portfolio,
                label = n),
            position = position_stack(vjust = 0.5),
            size = 6) +
  coord_flip() +
  labs (#title = "Number of Unique Attendees in Training & Development Sessions (2023)", # included in caption
        x = element_blank(),
        y = "Number of attendees") +
  theme_classic() +
  theme(
    title = element_text(size = 14, family="sans"),
    legend.text = element_text(size = 14, family="sans"),
    axis.text = element_text(size = 14, family ="sans"), 
    axis.title = element_text(size = 14, family = "sans") 
    ) +
  scale_fill_manual(
    values = "#90b8da"
  ) 
 # scale_x_discrete(
 #   labels = df_label$port_perc_label) 


ggsave(plot = last_plot(),filename = here::here("figures", "2023 unique attendance by portfolio.png"),
       width = 15, height = 9, dpi = 300)

```


## Overview of Research Training and Development Topics

Next, we explore the topics of the sessions in more detail. 
`r table_nums(name = "theme_overview", display = "cite")` shows the number 
of sessions and attendees by theme. The largest number of sessions offered was in the 
'Fund and Apply' theme, demonstrating Flinders University's commitment
to supporting researchers to attract research funding. The fact that this theme
also had the largest number of attendees is evidence that the research community
values these training and development opportunities. 

These numbers reflect the total number of attendees, most of whom are from Flinders 
(*n* = `r nrow(nrow(df_ienrol_att))`). 
 

```{r theme overview sp, include = TRUE, eval = TRUE}

#combine sessions & attendees per theme
theme_overview <- df_sp %>%
  group_by(Theme) %>%
  summarise(`Number of Sessions` = n(),
            `Number of Attendees` = sum(Attended))%>%
  arrange (desc(`Number of Attendees`)) %>% 
    adorn_totals("row")




# make it look good
kable(theme_overview, 
      booktabs = T,
      align = c('lcc'), 
      caption = "Training and Development Summary for 2023",
      linesep = "\\addlinespace") %>% 
  kable_styling(latex_options = c("hold_position", "striped")) 

```


```{r fund and apply 2023 by team, include = TRUE, eval = FALSE}

# [breadcrumb: This is very useful for working with the grants team, but does not need to be
  # part of this report. Pull out into its own Rmd.]

fund_23 <- df %>% 
  filter(Theme == "Fund and Apply") %>% 
  select (Attended, Session) %>% 
  relocate (Attended, .after = Session) %>% 
      mutate ("Number" = 1:n()) %>% 
    relocate (Number)

fund_team_23 <- fund_23 %>% 
  mutate(Team = case_when(
    grepl("NHMRC", Session) ~ "NHMRC", 
    grepl("ARC", Session) ~ "ARC", 
    grepl("MRFF", Session) ~ "MRFF", 
    TRUE ~ as.character("Other"))
  ) %>% 
  select (-Number) %>% 
  arrange(Team, desc(Attended)) %>% 
        mutate ("Number" = 1:n()) %>% 
    relocate (Number)
         

total_fund_team_23 <- sum(fund_team_23$Attended)

knitr::kable (
 fund_team_23 [, 1:3], # select only the names and levels columns
  booktabs = T,
   linesep = "",
  col.names = c("Session Number", "Session Name", "Number of Attendees"),
  caption =
    sprintf("Fund and Apply sessions in 2023 (n = %d)",
            total_fund_team_23),
  align = 'clc', 
  longtable = T #break the table over multiple pages
  ) %>%
   column_spec(1, width = "0.5in") %>% 
   column_spec(2, width = "5in") %>% 
  column_spec(3, width = "0.75in") %>% 
  pack_rows (index = table(fund_team_23$Team)) %>%
  kable_styling(full_width = F, 
                latex_options = c("repeat_header", "hold_position", "striped")) 

```

\newpage

`r table_nums(name = "sessions_by_theme", display = "cite")` provides 
additional detail about the specific sessions that we ran within each of the
training and development themes. 

```{r sessions and attendees by theme, include = TRUE, eval=TRUE}

# how many sessions per theme
theme_sessions <- df_sp %>%
  group_by(Theme) %>% 
  select(c(Theme, Session, Attended)) %>% 
  arrange(Theme) %>% 
  mutate(Theme = as.factor(Theme))

# make it look good
kable(theme_sessions [, 2:3],
  booktabs = T,
  linesep = "\\addlinespace",
  col.names = c("Sessions by Themes", "Number of Attendees"),
  caption =
    sprintf("Training and Development sessions for 2023 (n = %d)",
            n_attended_sp),
  align = 'lr', 
  longtable = T #break the table over multiple pages
  ) %>%
  column_spec(1, width = "5in") %>% 
  column_spec(2, width = "1in") %>% 
  pack_rows (index = table(theme_sessions$Theme),
               latex_gap_space = "0.4em",) %>%
    kable_styling(
    full_width = F,
    latex_options = c("repeat_header", "hold_position", "striped")
  ) 

```

\vskip 0.2in

```{r sessions and attendees by College params, include = TRUE, eval=TRUE}

# the parameters will sort it according to the College we indicate in the header

data(list = params$portfolio)

# the ienrol data doesn't have the theme, so we can't report on attendance by theme

# how many attendees at each session
session_att <- df_ienrol_att %>%
  select(c(course_name, event_num, fan, portfolio)) %>% 
  count(course_name, event_num)

session_att_college <- df_ienrol_att %>%
  filter(portfolio == "College of Education, Psychology and Social Work") %>% 
  count(course_name, .drop= FALSE) %>% 
  select(c(course_name, n)) %>% 
  rename("n_college" = "n")

# make it look good
kable(session_att [, c(1,4)],
  booktabs = T,
  linesep = "\\addlinespace",
  col.names = c("Sessions", "Number of Attendees"),
  caption =
    sprintf("Training and Development sessions for 2023 (n = %d)",
            n_attended_sp),
  align = 'lr', 
  longtable = T #break the table over multiple pages
  ) %>%
  column_spec(1, width = "5in") %>% 
  column_spec(2, width = "1in") %>% 
    kable_styling(
    full_width = F,
    latex_options = c("repeat_header", "hold_position", "striped")
  ) 

```

\vskip 0.2in

If you have any questions or suggestions for additional training and development 
sessions, please contact Dr Jen Beaudry (Manager, Researcher Training, Development 
and Communication) in Research Development and Support. 
